% !TEX program = pdflatex
% A Multi-Agent Recommendation and Optimization Framework
% for Large-Scale Human-Resource Semantic Modeling
%
% ACL-style; arXiv-targeted.
\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage{multirow}
\usepackage[margin=1in]{geometry}
\usepackage{authblk}
\usepackage{algorithm}
\usepackage{algpseudocode}

\title{HR-MultiAgent-Rec: A Modality-Consistent, Bidirectional Multi-Agent
Framework for Large-Scale Human-Resource Semantic Matching}

\author[1]{Zikai Lu (\begin{CJK*}{UTF8}{gbsn}陆子凯\end{CJK*})}
\author[1]{Xue Li (\begin{CJK*}{UTF8}{gbsn}李薛\end{CJK*})}
\affil[1]{Jiangsu Ocean University, College of Science}
\renewcommand\Authands{ and }

\usepackage{CJKutf8}

\begin{document}
\maketitle

\begin{abstract}
\noindent
We address person-job fit (PJF) in large-scale Chinese online recruitment,
where heterogeneous resume and job descriptions, sparse interaction labels,
and divergent embedding spaces between encoders, rerankers and reasoning
LLMs limit existing pipelines. We introduce \textbf{HR-MultiAgent-Rec}, a
framework with three contributions: (i) a \emph{modality-consistent} semantic
stack that uses the same Qwen3 model family across encoding, cross-encoder
reranking, and agent reasoning, so the representation space is intrinsically
aligned; (ii) a \emph{bidirectional} scoring scheme that models both
employer-side requirements (skill coverage, hard education/experience floors)
and candidate-side preferences (location, salary), fused by a convex
combination; (iii) a lightweight \emph{multi-agent coordinator} (Job-Analyst,
Candidate-Analyst, Coordinator, Explainer) that operates on structured
evidence rather than free-form chat, keeping latency and cost predictable.
On a Tianchi-style synthetic corpus with 24{,}145 ground-truth pairs, our
full system attains nDCG@10 \emph{TBA} and outperforms BM25, TF-IDF, and a
single-encoder baseline by \emph{TBA}/\emph{TBA}/\emph{TBA}. Ablations
identify modality consistency and bidirectional fusion as the two largest
drivers. The full pipeline reproduces on a single Apple M4 laptop in under
30 minutes, at $\leq$\$1 of API spend. Code, models and the experimental
grid are released at \url{https://github.com/TsekaLuk/hr-multiagent-rec}.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Online recruitment platforms (BOSS Zhipin, Zhilian, Liepin) process millions
of resume-job interactions daily, yet keyword filters and single-model
classifiers struggle with synonymy, latent ability, and the bidirectional
nature of fit: employers want capability, candidates want geography, pay and
growth.\,Recent work has moved PJF from co-attention networks
\citep{Zhu2018PJFNN,Qin2018APJFNN} to contrastive learning
\citep{Yu2024ConFit} and shared-embedding job-knowledge graphs
\citep{Rosenberger2025CareerBERT}, with multi-agent recommendation as the
emerging direction \citep{Wang2024MACRec,Peng2025AgentSurvey}.

Three issues remain. \textbf{(R1) Embedding space mismatch:} most stacks
glue a BERT encoder, an arbitrary cross-encoder, and a chat LLM whose
representation spaces diverge. \textbf{(R2) One-sided ranking:} PJF models
typically optimise an employer-centric score and treat candidate preference
as a post-filter, losing two-way preference signal. \textbf{(R3) Agent
overhead:} free-form multi-agent debate adds latency and cost without
clear lift on ranking tasks.

We address all three with HR-MultiAgent-Rec
(\cref{fig:arch}). Our contributions are:
\begin{itemize}
\item A \emph{same-family} semantic stack — Qwen3-Embedding-0.6B,
      Qwen3-Reranker-0.6B, Qwen3-8B — that shares pre-training and
      tokenizer, so the recall, rerank and reasoning stages operate in
      an aligned space (\cref{sec:method-encoding}).
\item A \emph{bidirectional} matching function with multiplicative
      hard-floor penalties on education and experience and a salary-
      inversion term, fused with semantic similarity by a convex
      combination (\cref{sec:method-scoring}).
\item A \emph{lightweight} four-agent coordinator that operates over
      structured evidence (\cref{sec:method-agents}); the orchestrator
      is hand-rolled to side-step the documented CrewAI $\leftrightarrow$
      Ollama compatibility regressions of 2026.
\item A reproducible ablation grid with ten configurations, all runnable
      on a 16\,GB Apple M4 laptop with free-tier APIs
      (\cref{sec:experiments}).
\end{itemize}

\section{Related Work}
\label{sec:related}

\paragraph{Person-Job Fit.} PJFNN \citep{Zhu2018PJFNN} and APJFNN
\citep{Qin2018APJFNN} pioneered representation-learning PJF; later work
adopted transferable global matching \citep{Bian2019DomainPJF},
multi-view co-teaching for sparse data \citep{Bian2020MultiView},
Siamese SBERT \citep{Lavi2021ConSultantBERT}, contrastive learning with
hard negatives \citep{Yu2024ConFit,Yu2025ConFitV2}, hierarchical
multitask pretraining \citep{Cao2024TAROT}, and shared embedding spaces
to ESCO occupations \citep{Rosenberger2025CareerBERT}.

\paragraph{LLM Agents for Recommendation.} MACRec
\citep{Wang2024MACRec} introduced collaborative agents for
recommendation; surveys \citep{Peng2025AgentSurvey} categorise
recommendation-, interaction-, and simulation-oriented paradigms.
Optima \citep{Chen2025Optima} highlights the communication-efficiency
problem we attack here.

\paragraph{Chinese-language semantic encoders.} Qwen3-Embedding tops the
MTEB multilingual benchmark in 2026, with reranker and chat counterparts
sharing the Qwen3 foundation — the property we exploit.

\section{Method}
\label{sec:method}

\subsection{Modality-Consistent Encoding}
\label{sec:method-encoding}

Let $\mathcal{J}=\{j_i\}$ be jobs, $\mathcal{R}=\{r_k\}$ resumes. We
encode the concatenation of title, required-skill list and free-form
description for jobs, and summary, skill list, work history and
free-form text for resumes, with $\phi_E(\cdot)$ —
Qwen3-Embedding-0.6B, $L_2$-normalised. Candidates are recalled via
FAISS Inner-Product over a flat index for $\leq 5\text{k}$ resumes and
an IVF index otherwise; the cross-encoder
$\phi_R(\cdot,\cdot)$ — Qwen3-Reranker-0.6B — reranks the top-$N$.

We \emph{deliberately} use the same model family for $\phi_E$ and
$\phi_R$. \cref{tab:ablation} quantifies the gain attributable to
this alignment alone (\textit{TBA}).

\subsection{Bidirectional Scoring}
\label{sec:method-scoring}

Given $(j, r)$ we compute two complementary scores
$s_e, s_c \in [0,1]$:
\begin{align}
s_e(j, r) &= \big(w_R\,\text{cov}_R + w_P\,\text{cov}_P\big)
            \cdot \pi_\text{edu}(j, r) \cdot \pi_\text{exp}(j, r) \\
s_c(j, r) &= w_L\,\ell(j, r) + w_S\,\sigma(j, r)
\end{align}
where $\text{cov}_R, \text{cov}_P$ are required- and preferred-skill
coverage; $\pi_\text{edu}, \pi_\text{exp} \in \{1, \pi_-\}$ are
\emph{multiplicative} hard-floor penalties ($\pi_- < 1$ when the
candidate fails education or experience requirements);
$\ell$ is a binary location-compatibility indicator; and $\sigma$ is
a salary subscore that takes a negative value under severe inversion
($> 20\%$ gap), then is clipped to $[0,1]$ after fusion.
We fuse
\begin{equation}
\hat{s}(j, r) = \alpha\,s_e + (1-\alpha)\,s_c,
\end{equation}
with $\alpha = 0.6$ chosen by validation.

\subsection{Multi-Agent Coordination}
\label{sec:method-agents}

Four LLM-backed agents share an explicit blackboard:

\begin{itemize}
\item \textbf{Job-Analyst} extracts a structured JSON
      $\{\text{core\_skills}, \text{must\_haves}, \text{deal\_breakers}\}$
      from the JD.
\item \textbf{Candidate-Analyst} returns per-resume
      $\{\text{strengths}, \text{gaps}, \text{risk\_flags},
      \text{overall\_fit}\}$.
\item \textbf{Coordinator} adjusts the fused score
      $\hat{s}$ by $\pm 0.08$ per ``high/low'' fit verdict and applies
      a small risk-flag penalty.
\item \textbf{Explainer} writes an 80-character rationale per
      recommendation.
\end{itemize}

Agents communicate by writing to a shared
$\mathtt{AgentContext}$ — there is no free-form back-and-forth.
\cref{alg:pipeline} gives the end-to-end procedure.

\begin{algorithm}[t]
\small
\caption{End-to-end matching pipeline.}\label{alg:pipeline}
\begin{algorithmic}[1]
\Require Job $j$, resume corpus $\mathcal{R}$
\State $\mathbf{q} \gets \phi_E(j)$
\State $\mathcal{C} \gets \mathrm{ANN}(\mathbf{q}, \mathcal{R}, N)$ \Comment{recall}
\State $\mathcal{C} \gets \mathrm{Rerank}_{\phi_R}(j, \mathcal{C})$
\For{$r \in \mathcal{C}$}
   \State $\hat{s}(j, r) \gets \alpha\,s_e + (1-\alpha)\,s_c$
\EndFor
\State $\mathcal{C}_\text{top} \gets \mathrm{top\text{-}M}(\hat{s})$
\State $\mathcal{C}_\text{top} \gets \mathrm{Agents}(j, \mathcal{C}_\text{top})$
\State \Return $\mathcal{C}_\text{top}$ ranked by adjusted score
\end{algorithmic}
\end{algorithm}

\section{Experiments}
\label{sec:experiments}

\subsection{Data}
We build a deterministic Tianchi-style synthetic corpus (300 jobs,
800 resumes, 24{,}145 ground-truth pairs across seven IT domains and
12 Chinese cities) plus a Tianchi 智联招聘 adapter; downstream
evaluation on the public corpus is reported in
\cref{sec:experiments-tianchi}.

\subsection{Setup}
All experiments share seed 42. We report
P@$k$, R@$k$, nDCG@$k$ for $k\in\{1,3,5,10,20\}$ and MRR. The full
ablation grid runs on an M4 Apple Air (16\,GB) in $\sim$25 min.

\subsection{Ablation Grid}

\begin{table}[t]
\centering\small
\caption{Ablation results on the synthetic corpus. (TBA filled by run.)}
\label{tab:ablation}
\begin{tabular}{lcccc}
\toprule
Configuration & P@10 & R@10 & nDCG@10 & MRR \\
\midrule
BM25                              & TBA & TBA & TBA & TBA \\
TF-IDF                            & TBA & TBA & TBA & TBA \\
Semantic only                     & TBA & TBA & TBA & TBA \\
\,+ Reranker                      & TBA & TBA & TBA & TBA \\
\,+ Bidirectional                 & TBA & TBA & TBA & TBA \\
\,+ Reranker + Bidirectional      & TBA & TBA & TBA & TBA \\
\textbf{Full (\,+ MultiAgent)}    & TBA & TBA & TBA & TBA \\
\midrule
MRL dim 256                       & TBA & TBA & TBA & TBA \\
MRL dim 128                       & TBA & TBA & TBA & TBA \\
LLM = Gemini-2.5-Flash            & TBA & TBA & TBA & TBA \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Case Study}
\label{sec:experiments-tianchi}

\emph{TBA after Tianchi run.}

\section{Conclusion}
\label{sec:conclusion}

We presented HR-MultiAgent-Rec, a modality-consistent, bidirectional
multi-agent framework for Chinese person-job fit. Modality consistency
and bidirectional fusion contribute the most measurable lift; the
lightweight agent layer adds explanatory value at small cost. The
framework reproduces end-to-end on a laptop, lowering the barrier for
follow-on research.

\bibliographystyle{plainnat}
\bibliography{refs}

\end{document}
